\begin{acknowledgements}
    This dissertation is a summary of my research in Utah State University and Siemens Corporate Research. In Utah State University, my research was under the guidance of my PhD advisor, Dr.~YangQuan Chan, and my Master advisor, Dr.~Kevin Moore. During my internship in Siemens Corporate Research, Dr.~Chellury Ram Sastry gave me many insightful advices. They always encourage me to focus on the fundamental problems and continuously improve my ideas by critical thinking. This is the best education experiences I have ever had in my life. I sincerely appreciate their time and efforts on helping me, including the PhD advices as well as the training on my mind.

    I feel really lucky since there are so many people who helped me on my research. Dr.~Dariusz Uci\'{n}ski, Dr.~Ren Wei, Dr.~Vladimeir Kulyukin and Dr.~Jacob Gunther gave me lots of valuable advices. The discussions with them really helped my research. Hereby I also appreciate my other committee members and past committee members, Dr.~Brandon Eames, Dr.~Matthew Berkemeier, and Dr.~Nick Flann.

    I want to sincerely thank all the people who had ever helped the MAS-net project, including the advisors, Dr.~Kevin Moore and Dr.~YangQuan Chen; the team members, PengYu Chen, ZhongMin Wang, Anisha Arora, HaiYang Chao and William Burgeous; the CSOIS members, Dr.~Lili Ma, Dr.~JinSong Liang, Dan Storment; Especially, I want to thank PengYu Chen for his significant contributions to the MAS-net project. Without him, the achievement is not possible.

    In the past several years, I have learned much from the discussions or collaborations with my colleagues. Hereby I present my appreciation to them. Nazif Cihan Tas, XiaoChun Xu, Vehbi Cagri Gungor. I am grateful for the various of help from my friends, Dr.~Hyo-Sung Ahn, Dr.~Dong Wei, Peng Zhao, Tian Xia, Michael Frashinger, Stanislava Soro.

\vspace{.2in}
\hfill Zhen Song
\end{acknowledgements}



